### 2016-07-27 paper/implementation.tex
refactor, add in lens context and puts

\subsection{SynthRWLessDNF}
We find an efficient way to synthesize DNF lenses which do not use rewrites.

>>>>

\subsection{SynthRewritelessDNF}
We find an efficient way to synthesize DNF lenses which do not use rewrites
through a clever encoding of the DNF regular expressions and examples.
A key insight into efficiently finding DNF lenses between two DNF regular
expressions is finding an ordering of DNF regular expressions which satisfy the
property such that, for two regular expressions $\DNFRegex$ and $\DNFRegexAlt$,
$\DNFRegex \leq \DNFRegexAlt$ and $\DNFRegexAlt \leq \DNFRegex$ if, and only if,
for some dnf lens $\DNFLens \OfType \DNFRegex \Leftrightarrow \DNFRegexAlt$,
with no use of \DNFRewriteLensRule{}.

\begin{definition}
$\DNFOf{\Sequence_1;\ldots\Sequence_n} \leq
\DNFOf{\SequenceAlt_1;\ldots\SequenceAlt_m}$
if $n<m$ or $n=m$ and
$sort([\Sequence_1;\ldots;\Sequence_n])\leq
sort([\SequenceAlt_1;\ldots;\SequenceAlt_n])$ by the dictionary ordering
on the sequence ordering.

$\SequenceOf{\String_0;\Atom_1;\ldots;\Atom_n;\String_n} \leq
\SequenceOf{\StringAlt_0;\AtomAlt_1;\ldots;\AtomAlt_n;\String_n}$
if $n<m$ or $n=m$ and
$sort([\Atom_1\ldots\Atom_n])\leq
sort([\AtomAlt_1\ldots\AtomAlt_n])$ by the dictionary ordering on the
atom ordering.

$\RegexVariable < \IterateLens{\DNFLens}$

$\RegexVariable \leq \RegexVariableAlt$ if
$\RegexVariable \leq \RegexVariableAlt$ as strings.

$\StarOf{\DNFRegex} \leq \StarOf{\DNFRegexAlt}$ if $\DNFRegex \leq \DNFRegexAlt$.
\end{definition}

\begin{theorem}
$\DNFRegex\leq\DNFRegexAlt$ and $\DNFRegexAlt\leq\DNFRegex$ if, and only
if there exists a $\DNFLens \OfType \DNFRegex \Leftrightarrow \DNFRegexAlt$.
\end{theorem}

Beyond that, we can use these orderings to find the lenses.
If $\DNFOf{\Sequence_1;\ldots;\Sequence_n}\leq\DNFOf{\SequenceAlt_1;\ldots;\SequenceAlt_n}$,
and $\DNFOf{\SequenceAlt_1;\ldots;\SequenceAlt_n}\leq\DNFOf{\Sequence_1;\ldots;\Sequence_n}$,
then $\Sort([\Sequence_1;\ldots;\Sequence_n])\leq\Sort([\Sequence_1;\ldots;\Sequence_n])$
using the dictionary ordering, which means that
$\Sort([\Sequence_1;\ldots;\Sequence_n])[i]\leq
\Sort([\SequenceAlt_1;\ldots;\SequenceAlt_n])[i]$ and
$\Sort([\SequenceAlt_1;\ldots;\SequenceAlt_n])[i]\leq
\Sort([\Sequence_1;\ldots;\Sequence_n])[i]$, which means that there is a
sequence lens between them.
\afm{I can keep going on about this stuff, should it go here?  Should I just make a brief claim
about it and move on}

Unfortunately, while this can find a well typed DNF regular expression, it doesn't
necessarily find the one that matches the examples.  In the situation where
there are multiple valid sorted orderings, there are multiple different lenses
with potentially different semantics.  Instead of iterating through all the
possible sortings, and finding one that matches the examples, we would like to
be able to immediately find only a sorting which satisfies the examples.

The key insight here is that certain invariants must hold for a DNF lens to have
semantics which match the examples.

\begin{enumerate}
\item If a source example string matches one of the clauses during parsing,
it must be sent to the clause the target example string matches during parsing.
\item If a source example string matches a user defined regular expression during
parsing, the target must match the exact same string during parsing.
\item If a source example string matches an iteration, then the target must iterate
the same number of times, and all the invariants must hold for each iterated part.
\end{enumerate}

This is done by joining additional parsing information alongside the regular
expression components.
